---
title: "lab_8_206"
author: "Sarah Rohlfing"
date: "11/15/2021"
output: html_document
---

```{r setup, include=FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

#attach
library(stargazer)
library(tidyverse)
library(broom)
library(modelsummary)
library(here)
library(corrplot)
library(janitor)
```

```{r}
homes <- read_csv(here("data","slo_homes.csv")) %>% 
  clean_names()
```
unique(homes$city) down in the console
make a subset called homes_sub that only contains obs. (rows) where the city is:

```{r}
homes_sub <- homes %>% 
  filter(city %in% c("San Luis Obispo", "Arroyo Grande", "Atascadero", "Santa Maria-Orcutt"))
```

## Do a little exploring of our data
sum statistics (home price, based on city and sale status)
```{r}
homes_sub %>% 
  group_by(city, status) %>% 
  summarise(mean_price = mean(price, na.rm = TRUE), 
            sd_price = sd(price, na.rm = TRUE))

# if you don't even want the code to run: eval = FALSE

ggplot(data = homes_sub, aes(x = price))+
  geom_density(aes(color = city, fill = city), alpha = 0.2)+
  scale_x_continuous(limits = c(0, 3e6))
```

explore the relationship (visual data exploration)btwn square footage and home price.
```{r}
ggplot(data = homes_sub, aes(x = sq_ft, y = price))+
  geom_jitter(aes(color = city, shape = city))+
  geom_smooth(method = lm)
  
```


## model the relationship with home price as DV

```{r}
homes_lm1 <- lm(price ~ city + bedrooms + bathrooms + sq_ft + price_per_sq_ft + status, data = homes_sub)

## 
homes_quant <- homes_sub %>% 
  select(price:price_per_sq_ft)

homes_cor <- cor(homes_quant)
homes_cor

corrplot(homes_cor, method = 'ellipse')

homes_lm1

#  diagnostic plots
plot(homes_lm1)

```

```{r}
#another model where we simplify

homes_lm2 <- lm(price ~ sq_ft + status + city, data = homes_sub)



plot(homes_lm2)
```
summary(homes_lm1)

adjusted r2red : .84 means 84 percent of variance in home price is explained by these variables. another 16 percent is missing. maybe add proximity to water? you will never have perfect variance. not good of bad, it just is what it is. 

summary(homes_lm2)
AIC can give us quantitative measure as to how much we it fits

```{r}
#find aic value aof each model, lower values indicate better balance between fit and complexity

AIC(homes_lm1)
AIC(homes_lm2)

#we still have major concerns about first model, maybe neither is what you want
```


```{r}
homes_lm3 <- lm(price ~ city + bedrooms + sq_ft + price_per_sq_ft + status, data = homes_sub)
plot(homes_lm3)
AIC(homes_lm3)
summary(homes_lm3)
```

## use 'modelsummary' to show model outputs side-by-side:
if you use model summary to return model outputs of multiple models, it wants you to feed it to it as a list

```{r}
modelsummary(list(homes_lm1, homes_lm2, homes_lm3))
```

## start making predictions with this model

use 'broom::augmant()'

```{r}
homes_predict <- augment(homes_lm1)
```


'predict()' function to try to predict your model on new scenarios that you create. 
```{r}

```
